---
title: "Plotting DAPS results"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting DAPS results}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This vignette demonstrates how to visualize posterior inclusion probabilities (PIPs), signal clusters and credible sets from **DAPS** using the `daps_plot()` function.

The main plotting function produces a two-panel figure:

1. **Top panel**: SNP-level posterior inclusion probabilities
2. **Bottom panel**: Signal clusters or credible sets, showing cluster indices on the left and cluster-level posterior probabilities (CPIP) or coverage probabilities on the right

## Example

We illustrate the workflow using the `N3finemapping` example dataset from **susieR**. DAPS can visualize these results directly:

```{r fig.alt='DAPS plot example'}
library(DAPS)
library(susieR)

X <- N3finemapping$X
Y <- N3finemapping$Y[, 1]
fitted <- daps(X, Y, L = 10)

daps_plot(fitted)
```

## Summary

The `daps_plot()` function provides a clear and compact visualization of fine-mapping results, making it easy to explore:

- SNP-level PIP patterns
- Signal clusters or credible sets
- CPIP or coverage probabilities

This enables effective interpretation of DAP-S or SuSiE output in genomic studies.
